You can be Shakespeare! \\ A Case Study in Paraphrase Targeting Writing Styles

### 2012-08-26 paper/paper.tex
further progres...

In this paper, we investigate the task of automatic paraphrasing when targeting a writing style, focusing specifically on the style of Early Modern English employed by William Shakespeare.
We exploit modern translations of 17 plays written to help students better understand Shakespeare's work.  A parallel corpus is extracted from these modern translations,
which is then used to train phrase-based translation models which are capable of automatically paraphrasing ordinary sentences into Shakesperean English.  In addition we develop several
baseline systems which don't make use of this source of parallel text and instead rely on dictionaries of expressions commonly found in Shakesperean english, or parallel monolingual text
gathered through Amazon's Mechanical Turk \cite{chen11}.

We evaluate these models both through human judgements and standard evaluation metrics from the Machine Translation and paraphrase literature, however no previous work has investigated the ability of these automatic metrics
to capture the notion of writing style.  We propose several new metrics for evaluating paraphrases targeting a specific writing style, and measure correlation with human judgements showing  promising, yet
preliminary results.

Systems which are capable of automatically paraphrasing literary writing styles could be directly benefical for educational applications, for example helping students to experiment with writing literature in the
style of authors they are studying.  Additionally note that out of the 37 surviving plays written by William Shakespeare, only 17 currently have modern translations available; although we have not yet formally evaluated
paraphrasing in the other direction, we believe this work also has the potential to make the other 20 plays more accessable to students of Shakespeare by automatically generating relatively high-quality modern translations.

@@

\section{Data}
We propose to use Shakespeare's plays as a testbed for the task of paraphrasing while targeting a specific writing style.  Because these plays are some of the
highest regarded examples of English literature and are also very unique in style, many linguistic resources are available such as parallel corpora
of modern translations and dictionaries of stylistically representative words and their modern equivelants.

@@

@@

\begin{table}[ht]
  \begin{center}
    \begin{tabular}{|l|p{3in}|}
      \hline
      System & Description \\
      \hline
      \hline
      16and7plays\_36LM & Phrase table learned from all 16 Sparknotes plays (other than R\&J) and language model built from all 36 of Shakespeare's plays, excluding R\&J.
      Uses default Moses parameters. \\
      \hline
      16and7plays\_36LM\_MERT & Same as 16and7plays\_36LM except parameters are tuned using Minimum Error Rate Training instead of using the default Moses parameters.\\
      \hline
      16and7plays\_16LM & Phrase table is built from both Sparknotes and Enotes data, and Language model is built from the 16 with modern translations\\
      \hline
      16and7plays\_16LM\_MERT & Same as 16and7plays\_16LM except parameters are tuned using MERT. \\
      \hline
      16plays\_36LM & Only Sparknotes modern translations are used.  All 36 plays are used to train Shakesperean language model. a\\
      \hline
      16plays\_36LM\_MERT & Same as 16plays\_36LM except parameters are tuned using MERT. \\
      \hline
      modern (no change) & No changes are made to the input, modern translations are left unchanged. \\
      \hline
      Dictionary & Dictionary baseline described in section \ref{dictionary_baseline}\\
      \hline
    \end{tabular}
  \end{center}
  \caption{Descriptions of various systems for Shakesperean Paraphrase.  Romeo and Juliet is held out for testing.}
  \label{systems}
\end{table}

\begin{figure}[ht]
  \begin{center}
    \begin{tabular}{cc}
      \includegraphics[width=2.4in]{figures/bleupinc1.pdf} & \includegraphics[width=2.4in]{figures/bleupinc2.pdf} \\
    \end{tabular}
  \end{center}
  \caption{Various Shakesperean Paraphrase systems compared using BLEU and PINC.}
  \label{bleupinc}
\end{figure}

@@

\begin{table}
  \begin{center}
    \begin{tabular}{|l|l|p{1.4in}|p{1.4in}|}
      \hline
      Source & Speaker & Input & Output \\
      \hline
      \hline
      Romeo \& Juliet & Benvolio & he killed your relative , brave mercutio , and then young romeo killed him . & he slew thy kinsman , brave mercutio , and then young romeo kill him . \\
      \hline
      Romeo \& Juliet & Romeo & i can read my own fortune in my misery . & i can read mine own fortune in my woes . \\
      \hline
      Star Wars & Palpatine & If you will not be turned, you will be destroyed! & if you will not be turn 'd , you will be undone ! \\
      \hline
      Star Wars & Luke & Father, please! Help me! & father , i pray you , help me ! \\    
      \hline
      The Matrix & Agent Smith & Good bye, Mr. Anderson. & fare you well , good master anderson . \\
      \hline
      The Matrix & Morpheus & I'm trying to free your mind, Neo. But I can only show you the door. You're the one that has to walk through it. & i 'll to free your mind , neo. but i can but show you the door. you 're the one that hath to tread it . \\
      \hline
      Raiders of the Lost Ark & Belloq & Good afternoon, Dr. Jones. & well met , dr. jones . \\
      \hline
      Raiders of the Lost Ark & Jones & I ought to kill you right now. & i should kill thee straight . \\
      \hline
    \end{tabular}
  \end{center}
  \caption{Example Shakesperean paraphrases generated by the best overall system.}
\end{table}

@@

Based on the human evaluation, it appears that the baseline based on the paraphrase data collected by asking Mechanical Turk users to
describe videos \cite{chen11} has the highest semantic adequacy, however it is also fairly conservative making few changes to the input.
The dictionary baseline, and system trained on parallel modern translations make a roughly comparable number of changes to the input
sentences, but the system trained on modern translations achieves higher semantic adequacy, while being rated higher on style and overall.

These results seem roughly in line with the automatic evalution metrics presented in figure \ref{bleupinc}, however with several important
differences.  Although the video baseline achieves the highest semantic adequacy in the human evaluation, it's BLEU score
is significantly lower than 16plays\_36LM on the Sparknotes data.\footnote{
Note that the BLEU score of 16plays\_36LM is significantly lower when evaluated on the Enotes data.  This makes sense, because the 
16 plays come from Sparknotes. This system is not trained on the 7 Enotes plays which, whose modern translations tend
to be slightly different in style.}
It would appear that in our case BLEU is conflating semantic adequecy with writing style.  Although the paraphrases produced 
by the video baseline have high semantic adequacy, their style tends to differ from the reference translations resulting
in fewer ngram matches, and thus a lower BLEU score.

\begin{figure}
  \begin{center}
    \includegraphics[width=4in]{figures/human_judgements.pdf}
  \end{center}
  \caption{Average human judgements evaluating semantic adequacy, lexical dissimilarity, stylistic similarity, and overall quality
    of Shakesperean paraphrase systems} 
  \label{human_judgements}
\end{figure}

\section{Automatic Metrics Evaluating Writing Style}
While PINC and BLEU do seem useful for automatically evaluating writing styles, BLEU tends to conflate the notions of
semantic adequacy with writing style.  When comparing various systems using automatic metrics, however, it would seem useful
to seperate these two critera.  It would seem desirable for our automatic evaluation metrics to be able to distinguish
between a system which generates perfect paraphrases which don't match the target style of writing and a system which
generates sentences in the correct style, but which convey different meaning.

@@

\begin{figure}
  \begin{center}
    \includegraphics[width=4in]{figures/style_metrics.pdf}
    \end{center}
    \caption{Overall results from comparing automatic style metrics.  Note that the automatic metrics agree with results from human judgements in figure \ref{human_judgements}.}
    \label{style_metrics}
\end{figure}

@@

Much previous work has addressed the task of automatically generating paraphrases \cite{Callison-Burch08,Kok10}.  In addition several authors have previously proposed 
automatic paraphrase evaluation metrics \cite{Callison-Burch08b,Bangalore00,liu10}.
We are not aware, however, of any previous work that has addressed the task of generating or evaluating
paraphrases targeting a specific style of writing.

@@

\section{Conclusions}

>>>>

In this paper, we investigate the task of automatic paraphrasing when targeting a writing style, focusing specifically on the style of Early Modern English employed by William Shakespeare.
We exploit modern translations of 17 plays written to help students better understand Shakespeare's work.  A parallel corpus is extracted from these modern translations,
which is then used to train phrase-based translation models which are capable of automatically paraphrasing ordinary sentences into Shakesperean English.  In addition we develop several
baseline systems which do not make use of this source of parallel text and instead rely on manually compiled dictionaries of expressions commonly found in Shakesperean english, or out of
domain parallel monolingual text gathered through Amazon's Mechanical Turk \cite{chen11}.

We evaluate these models both through human judgements and standard evaluation metrics from the Machine Translation and paraphrase literature, however no previous work has investigated the ability of automatic
evaluation metrics to capture the notion of writing style.  We propose several new metrics for evaluating paraphrases targeting a specific writing style, and measure correlation with human judgements showing  promising
preliminary results.

Systems which are capable of automatically paraphrasing literary writing styles could be directly benefical for educational applications.  For example, a system which generates paraphrases targeting a specific style
of writing could help students to experiment with writing literature in that style.
In addition, out of the 37 surviving plays written by William Shakespeare only 17 currently have modern translations available.  Though we have not yet formally evaluated
paraphrasing Shakespeare's plays into modern English, we believe it should be possible to make the other 20 plays more accessable to students of Shakespeare by automatically 
generating high-quality modern translations.

@@

\section{Shakesperean Paraphrasing}
We propose to use Shakespeare's plays as a testbed for the task of paraphrasing while targeting a specific writing style.  Because these plays are some of the
highest regarded examples of English literature and are also very unique in style, many linguistic resources are available such as parallel corpora
of modern translations and dictionaries of stylistically representative words and their modern equivelants.

@@

We apply a typical phrase-based Statistical Machine Translation pipeline, performing
word alignment on the data described in table \ref{corpus_stats} using GIZA++ \cite{Och03}, then extracting phrase pairs and performing decoding using Moses \cite{Koehn07}.

@@

\begin{table}[ht]
  \begin{center}
    \begin{tabular}{|l|p{3in}|}
      \hline
      System & Description \\
      \hline
      \hline
      16and7plays\_36LM & Phrase table learned from all 16 Sparknotes plays (other than R\&J) and language model built from all 36 of Shakespeare's plays, excluding R\&J.
      Uses default Moses parameters. \\
      \hline
      16and7plays\_36LM\_MERT & Same as 16and7plays\_36LM except parameters are tuned using Minimum Error Rate Training \cite{MERT} instead of using the default Moses parameters.\\
      \hline
      16and7plays\_16LM & Phrase table is built from both Sparknotes and Enotes data, and Language model is built from the 16 with modern translations\\
      \hline
      16and7plays\_16LM\_MERT & Same as 16and7plays\_16LM except parameters are tuned using MERT. \\
      \hline
      16plays\_36LM & Only Sparknotes modern translations are used.  All 36 plays are used to train Shakesperean language model. a\\
      \hline
      16plays\_36LM\_MERT & Same as 16plays\_36LM except parameters are tuned using MERT. \\
      \hline
      modern (no change) & No changes are made to the input, modern translations are left unchanged. \\
      \hline
      Dictionary & Dictionary baseline described in section \ref{dictionary_baseline}\\
      \hline
    \end{tabular}
  \end{center}
  \caption{Descriptions of various systems for Shakesperean Paraphrase.  Romeo and Juliet is held out for testing.}
  \label{systems}
\end{table}

\begin{figure}
  \begin{center}
    \begin{tabular}{cc}
      \includegraphics[width=2.4in]{figures/bleupinc1.pdf} & \includegraphics[width=2.4in]{figures/bleupinc2.pdf} \\
    \end{tabular}
  \end{center}
  \caption{Various Shakesperean Paraphrase systems compared using BLEU and PINC.  A brief description of each system is presented in table \ref{systems}.}
  \label{bleupinc}
\end{figure}

\begin{table}[ht]
  \begin{center}
    \begin{tabular}{|l|l|p{1.4in}|p{1.4in}|}
      \hline
      Source & Speaker & Input & Output \\
      \hline
      \hline
      Romeo \& Juliet & Benvolio & he killed your relative , brave mercutio , and then young romeo killed him . & he slew thy kinsman , brave mercutio , and then young romeo kill him . \\
      \hline
      Romeo \& Juliet & Romeo & i can read my own fortune in my misery . & i can read mine own fortune in my woes . \\
      \hline
      Star Wars & Palpatine & If you will not be turned, you will be destroyed! & if you will not be turn 'd , you will be undone ! \\
      \hline
      Star Wars & Luke & Father, please! Help me! & father , i pray you , help me ! \\    
      \hline
      The Matrix & Agent Smith & Good bye, Mr. Anderson. & fare you well , good master anderson . \\
      \hline
      The Matrix & Morpheus & I'm trying to free your mind, Neo. But I can only show you the door. You're the one that has to walk through it. & i 'll to free your mind , neo. but i can but show you the door. you 're the one that hath to tread it . \\
      \hline
      Raiders of the Lost Ark & Belloq & Good afternoon, Dr. Jones. & well met , dr. jones . \\
      \hline
      Raiders of the Lost Ark & Jones & I ought to kill you right now. & i should kill thee straight . \\
      \hline
    \end{tabular}
  \end{center}
  \caption{Example Shakesperean paraphrases generated by the best overall system.}
\end{table}

@@

@@

Based on the human evaluation, it appears that the baseline combining paraphrases collected from mechanical turk \cite{chen11} with
a Shakesperean language model has the highest semantic adequacy, however it is also fairly conservative making few changes to the input.
The dictionary baseline, and system trained on parallel modern translations make a roughly comparable number of changes to the input
sentences, but the system trained on modern translations achieves higher semantic adequacy, while being rated higher on style and overall.

These results seem roughly in line with the automatic evalution metrics presented in figure \ref{bleupinc}, however with several important
differences.  Although the video baseline achieves the highest semantic adequacy in the human evaluation, it's BLEU score
is significantly lower than 16plays\_36LM on the Sparknotes data.\footnote{
Note that the BLEU score of 16plays\_36LM is significantly lower when evaluated on the Enotes data.  This makes sense, because the 
16 plays come from Sparknotes. This system is not trained on the 7 Enotes plays which, whose modern translations tend
to be slightly different in style.}
It would appear that in this case BLEU is conflating semantic adequecy with writing style.  Although the paraphrases produced 
by the video baseline have high semantic adequacy, their style tends to differ from the reference translations resulting
in fewer ngram matches, and thus a lower BLEU score.

\begin{figure}
  \begin{center}
    \includegraphics[width=5in]{figures/human_judgements.pdf}
  \end{center}
  \caption{Average human judgements evaluating semantic adequacy, lexical dissimilarity, stylistic similarity, and overall quality
    of Shakesperean paraphrase systems} 
  \label{human_judgements}
\end{figure}

\section{Automatic Metrics Evaluating Writing Style}
While PINC and BLEU do seem useful for automatically evaluating paraphrases targeting a  writing style, BLEU tends to conflate the notions of
semantic adequacy with writing style.  When comparing various systems using automatic metrics, however, it would seem useful
to seperate these two critera.  It would seem desirable for our automatic evaluation metrics to be able to distinguish
between a system which generates perfect paraphrases which don't match the target style of writing and a system which
generates sentences in the correct style, but which convey different meaning.

@@

\begin{figure}
  \begin{center}
    \includegraphics[width=5in]{figures/style_metrics.pdf}
    \end{center}
    \caption{Overall results from comparing automatic style metrics.  Note that the automatic metrics agree with results from human judgements in figure \ref{human_judgements}.}
    \label{style_metrics}
\end{figure}

@@

Much previous work has addressed the task of automatically generating paraphrases \cite{Barzilay03,dolan04,Shinyama03,Das09,bannard05,Callison-Burch08,Kok10}.  In addition several authors have previously proposed 
automatic paraphrase evaluation metrics \cite{chen11,Callison-Burch08b,Bangalore00,liu10}.
We are not aware, however, of any previous work that has addressed the task of generating or evaluating
paraphrases targeting a specific style of writing.

@@

\section{Conclusions}
We have presented initial investigation into the task of automatic paraphrasing while targeting a specific style of writing.  We proposed Shakespere's plays and their
modern translations as a tesbed for this task, and developed a series of paraphrase systems targeting Shakesperean English.  We showed that while existing evaluation
metrics are useful for evaluating paraphrases in this context, BLEU tends to conflate semantic equivelance with writing style giving an incomplete picture of which systems
perform better according to each of these critera.

To address the problems we have demonstrated with previous evaluation metrics applied to this task, we have introduced two new metrics for evaluating writing style.
We measured correlation between automatic metrics and human judgements in the context of paraphrasing writing style, and showed
that our new metrics have better correlation with human judgements than existing metrics in the context of our data.
While this evaluation is limited to one specific style of writing, we are optimistic that these or similar metrics will also perform well when
evaluating other writing styles.

Future work could include automatically translating the remaining 20 of Shakespeare's plays into modern English, which could be benefical to students
of Shakespere's plays and also to future human translators.
